Supplementary Material for ``Evaluating infectious disease forecasts with allocation scoring rules''

### 2023-12-07 alloscore_manuscript/supplement.rnw
slowly tying the logic of secs 4 and 5 together

The constraint now determines $\tau$ (and hence the Bayes act) through $\sum_{i=1}^{N} q_{\tau,F_i} = K.$
This equation can be restated as the requirement that 
\begin{align}
K \in TQ_F(\tau) \label{eqn:tau-inclusion}
\end{align}
where the set-valued function
\begin{align}
TQ_F(\tau) := \sum_{i=1}^{N} Q_{F_i}(\tau) = \left[\sum_{i=1}^{N} q^{-}_{\tau,F_i}, \sum_{i=1}^{N} q^{+}_{\tau,F_i}\right]
\end{align}
is defined using interval addition $[a,b] + [c,d] = [a+c, b+d]$. (Note that the letter $T$ is being used to connote a ``totalling'' 
operation, as it often is in survey sampling literature.)

@@

@@

Iterating this process we obtain a sequence $\{I_k\}, k=1,2,\ldots$ of intervals of widths 
$\left|I_k \right| = 2^{1-k}\left|I_1 \right|$ which either terminates at one of the scenarios 
($\bullet$), ($\bullet\!-$), or ($-\!\bullet$), or provides infinite sequences $\{\tau_{L,k}\}$ and $\{\tau_{U,k}\}$ converging
to $\tau^{\star}$ from below and above. Note that this algorithm is somewhat more delicate than the corrsponding ``bisection'' algorithm 
for finding a root of $F_T(x) - \tau$ for a given $\tau$.

>>>>

The constraint now determines $\tau$ (and hence the Bayes act) through 
\begin{align}
\sum_{i=1}^{N} q_{\tau,F_i} = K. \label{eqn:quantiles-sum-to-K}
\end{align}
This equation implies that 
\begin{align}
K \in TQ_F(\tau) \label{eqn:tau-inclusion}
\end{align}
where the set-valued function
\begin{align}
TQ_F(\tau) := \sum_{i=1}^{N} Q_{F_i}(\tau) = \left[\sum_{i=1}^{N} q^{-}_{\tau,F_i}, \sum_{i=1}^{N} q^{+}_{\tau,F_i}\right]
\end{align}
is defined using interval addition $[a,b] + [c,d] = [a+c, b+d]$. (Note that the letter $T$ is being used to connote a ``totalling'' 
operation, as it often is in survey sampling literature.) Conversely, if $\tau^{\star}$ satisfies \eqref{eqn:tau-inclusion}, then
we can find a solution $\bm{q}_{\tau^{\star},F} := (q_{\tau^{\star},F_1},\ldots,q_{\tau^{\star},F_N})$ to 
\eqref{eqn:quantiles-sum-to-K} within the set 
$\undertilde{\bm{F}}^{-1}(\tau^{\star}) \subset \mathbb{R}_{+}^N$ where $\undertilde{\bm{F}}^{-1}(\tau)$  is the 
Cartesian product $(F_1^{-1}(\tau),\ldots,F_N^{-1}(\tau))$.

@@

Exact computation of the allocation score $S_A(F, y; K)$ of a forecast $F$ requires an explicit choice of and expression for a 
solution $\bm{q}_{\tau^{\star},F} \in \undertilde{\bm{F}}^{-1}(\tau^{\star})$ to \eqref{eqn:quantiles-sum-to-K} where
$\tau^{\star}$ solves \eqref{eqn:tau-inclusion}. For practical scenarios in which the forecast $F$ has a form preventing 
analytical solutions to \eqref{eqn:quantiles-sum-to-K}, we must develop a method to approximate solutions to \eqref{eqn:tau-inclusion}
which lead to adequate approximations of the linear program
\begin{align}
\sum_{x \in \undertilde{\bm{F}}^{-1}(\tau^{\star})}x_i = K.
\end{align}

@@

Iterating this process we obtain a sequence $\{I_k\}, k=1,2,\ldots$ of intervals of widths 
$\left|I_k \right| = 2^{1-k}\left|I_1 \right|$ which either terminates at one of the scenarios 
($\bullet$), ($\bullet\!-$), or ($-\!\bullet$), or provides infinite sequences $\{\tau_{L,k}\}$ and $\{\tau_{U,k}\}$ converging
to $\tau^{\star}$ from below and above. Such a sequence provides the basis of a ``bisection'' algorithm for finding
the ``root'' $\tau^{\star}$ of the set condition $0 \in TQ_F(\tau) - K$.
